Heuristics for the Score-Constrained Strip-Packing Problem

### 2018-05-10 PAPER/main.tex
changed word 'packed' in algorithm to italics
added pseudocode for mffd algorithm

\begin{theorem}
	\label{thm:copsoln}
	There exists a feasible solution $\mathcal{T}$ to an instance $\mathcal{M}$ of the COP if and only if its corresponding graph $G=(V, B\cup R)$ contains an alternating Hamiltonian cycle.
\end{theorem}
\begin{proof}
	Let $\mathcal{A} = \{v_1, v_2, ..., v_{2n+1}, v_{2n+2}\}$ be an alternating Hamiltonian cycle on $G$, where $v_{2n+1}$ and $v_{2n+2}$ are the dominating vertices. By definition, $\mathcal{A}$ contains all vertices on $G$, and all $n+1$ edgs in $B$. Thus, there exists a set of $n+1$ edges from $R$ that, together with the edges in $B$, form the alternating Hamiltonian cycle. Now, removing the dominating vertices and any incident edges gives rise to an alternating Hamiltonian path $\mathcal{A}' = \{v_1, v_2, ..., v_{2n-1}, v_{2n}\}$, whose first edge $(v_1, v_2)$ and last edge $(v_{2n-1}, v_{2n})$ are in $B$. The order of the values corresponding to each vertex of this path form a feasible solution $\mathcal{T}$, where values that are partners make up a tuple.\qed
\end{proof}

@@

\begin{algorithm}[H]
	\caption{MFFD$^+$}
	\label{alg:mffd+}
	\begin{algorithmic}[1]
		\State Sort items in $\mathcal{I}$ in order of non-increasing widths $w_i$.
		\For{$i \gets 1 \To |\mathcal{I}|$}
			\State $j \gets 1$, packed $\gets \False$
			\While{not packed}
				\If{$S_j \in \mathcal{S}$ and $\sum_{i=1}^{|S_j|}w_i + w_i \leq W$}
					\State Run AHC
					\If{AHC returns feasible solution}
						\State $S_j \gets S_j \cup i$ in order of feasible solution
						\State packed $\gets \True$
					\Else \hspace{0.2mm} $j \gets j + 1$					 
					\EndIf
				\ElsIf{$S_j \notin \mathcal{S}$}
					\State $S_j \gets S_j \cup i$ in regular orientation
					\State $\mathcal{S} \gets \mathcal{S} \cup S_j$	
					\State packed $\gets \True$
				\EndIf
			\EndWhile	
		\EndFor
		\Return $\mathcal{S}$
	\end{algorithmic}	
\end{algorithm}

\section{Comparison}
\begin{itemize}
	\item Heuristics implemented in C++ and executed on a computer equipped with an Intel Core i3-2120 processor with a frequency of 3.30GHz.
	\item $n$ = 100, 500, and 1000, number of items in $\mathcal{I}$, $W$ = 5000, 2500, 1250, item widths uniform dist [150, 1000], score widths uniform dist [1,70] (ensures each item has two score widths that do not overlap), all items and strips have height H ( = 1)
	\item Changing strip length changes the average number of items per strip (why is this important?) Harder problems have fewer items per strip
	\item run each instance 1000 times (per value of $\delta$), same instances each time.
	\item table shows optimality, which is the number of strips in the final solution generated by the heuristic divided by the number of strips in the optimal solution (which is calculated using the lower bound for $k$ above), =1 then optimal
	\item Goulimis stated n= 10, this is able to find solutions for n=1000
	\item graph showing time or optimality of all three heuristics
	\item $\delta$ is proportion of score widths that meet VSC (excluding partners and itself), 0.1 increments.
	\item changing the value of $\tau$ changes the proportion of the number of score widths
	\item if $\delta = 0.0$, then no score widths can be aligned number of strips = $n$, $\delta = 1.0$, then all score widths can be aligned with any other score width, BPP.
	\item As the strip length is decreased, MFFD+ improves, number of items/strip decreases
	\item when $\delta = 1.0$ MFFD and MFFD+ will perform in the same manner (like original FFD)
	\item PS does not reach highest optimality at $\delta = 0.8$ onwards in any strip length
	\item as avg number of items per strip decreases, PS is less efficient, MFFD+ is better
	\item note anomaly in $n = 1000, W = 1250, \delta = 0.3$, MFFD performs the best.
\end{itemize}

>>>>

\begin{theorem}
	\label{thm:copsoln}
	If there exists an alternating Hamiltonian cycle on a graph $G$ created from an instance $\mathcal{M}$ of the COP, then AHC is able to find the cycle in $O(n^2)$ time.
\end{theorem}
\begin{proof}
	\qed
\end{proof}

@@

\begin{algorithm}[H]
\caption{MFFD}
\label{alg:mffd}
\begin{algorithmic}[1]
	\State Sort items in $\mathcal{I}$ in order of non-increasing widths $w_i$.
	\State Let $r_j$ denote the right-most score width on strip $S_j$.
		\For{$i \gets 1 \To |\mathcal{I}|$}
			\State $j \gets 1$, packed $\gets \False$
			\While{\textbf{not} packed}
				\If{$S_j \in \mathcal{S}$ and $\sum_{i=1}^{|S_j|}w_i + w_i \leq W$}
					\If{$r_j + a_i \geq \tau$}
						\State $S_j \gets S_j \cup (a_i, b_i)$
						\State packed $\gets \True$
					\ElsIf{$r_j + b_i \geq \tau$}
						\State $S_j \gets S_j \cup (b_i, a_i)$
						\State packed $\gets \True$
					\Else \hspace{0.2mm} $j \gets j + 1$		
					\EndIf
				\ElsIf{$S_j \notin \mathcal{S}$}
					\State $S_j \gets S_j \cup (a_i, b_i)$
					\State $\mathcal{S} \gets \mathcal{S} \cup S_j$
					\State packed $\gets \True$	
				\EndIf
			\EndWhile	
		\EndFor
	\Return $\mathcal{S}$
\end{algorithmic}	
\end{algorithm}

\begin{algorithm}[H]
\caption{MFFD$^+$}
\label{alg:mffd+}
\begin{algorithmic}[1]
	\State Sort items in $\mathcal{I}$ in order of non-increasing widths $w_i$.
	\For{$i \gets 1 \To |\mathcal{I}|$}
		\State $j \gets 1$, packed $\gets \False$
		\While{\textbf{not} packed}
			\If{$S_j \in \mathcal{S}$ and $\sum_{i=1}^{|S_j|}w_i + w_i \leq W$}
				\State Run AHC
				\If{AHC returns feasible solution}
					\State $S_j \gets S_j \cup i$ in order of feasible solution
					\State packed $\gets \True$
				\Else \hspace{0.2mm} $j \gets j + 1$					 
				\EndIf
			\ElsIf{$S_j \notin \mathcal{S}$}
				\State $S_j \gets S_j \cup i$ in regular orientation
				\State $\mathcal{S} \gets \mathcal{S} \cup S_j$	
				\State packed $\gets \True$
			\EndIf
		\EndWhile	
	\EndFor
	\Return $\mathcal{S}$
\end{algorithmic}	
\end{algorithm}

\section{Comparison}
\subsection{Problem Instances}
\begin{itemize}
	\item sets of items $\mathcal{I}$ of sizes 100, 500, and 100
	\item 1000 different problem instances for each size, so 1000 problem instances for $|\mathcal{I}| = 100$, $|\mathcal{I}| = 500$, and $|\mathcal{I}| = 1000$
	\item use the same 1000 instances in every run for each size, fair
	\item For all problem instances, the items have equal height $H = 1$.
	\item For each problem instance, the items have varying widths randomly selected from a uniform distribution between 150 and 1000, and score widths also randomly selected from a uniform distribution between 1 and 70, preventing the score widths from overlapping, and ensuring that each item has exactly two score widths.
	\item The strips also have equal height $H = 1$, and three different widths, $W = 5000$, $W = 2500$, and $W = 1250$. 
	\item As the strip width decreases, the number of items per strip decreases, making the problem more difficult.
	\item We introduce a parameter $\delta$ that gives the proportion of pairs of score widths whose total sum is greater than or equal to $\tau$. 
	\item Values for $\delta$ from 0.0 to 1.0 in increments of 0.1 are calculated by changing the value of $\tau$. 
	\item Thus, if $\delta  = 0.0$, then there are no score widths that can feasibly be aligned together, and hence $|\mathcal{I}|$ strips are required (one for each item), whereas if $\delta = 1.0$, then all pairs of score widths meet the vicinal sum constraint (i.e. sum of all pairs of score widths $\geq \tau$), and the problem is therefore analogous to the BPP. 
\end{itemize}

\begin{itemize}
	\item Heuristics implemented in C++ and executed on a computer equipped with an Intel Core i3-2120 processor with a frequency of 3.30GHz.
	\item $n$ = 100, 500, and 1000, number of items in $\mathcal{I}$, $W$ = 5000, 2500, 1250, item widths uniform dist [150, 1000], score widths uniform dist [1,70] (ensures each item has two score widths that do not overlap), all items and strips have height H ( = 1)
	\item Changing strip length changes the average number of items per strip (why is this important?) Harder problems have fewer items per strip
	\item run each instance 1000 times (per value of $\delta$), same instances each time.
	\item table shows optimality, which is the number of strips in the final solution generated by the heuristic divided by the number of strips in the optimal solution (which is calculated using the lower bound for $k$ above), =1 then optimal
	\item Goulimis stated n= 10, this is able to find solutions for n=1000
	\item graph showing time or optimality of all three heuristics
	\item $\delta$ is proportion of score widths that meet VSC (excluding partners and itself), 0.1 increments.
	\item changing the value of $\tau$ changes the proportion of the number of score widths
	\item if $\delta = 0.0$, then no score widths can be aligned number of strips = $n$, $\delta = 1.0$, then all score widths can be aligned with any other score width, BPP.
	\item As the strip length is decreased, MFFD+ improves, number of items/strip decreases
	\item when $\delta = 1.0$ MFFD and MFFD+ will perform in the same manner (like original FFD)
	\item PS does not reach highest optimality at $\delta = 0.8$ onwards in any strip length
	\item as avg number of items per strip decreases, PS is less efficient, MFFD+ is better
	\item note anomaly in $n = 1000, W = 1250, \delta = 0.3$, MFFD performs the best.
\end{itemize}
